Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-21 snapshot_system/background.tex

The previous work for storage backup has extensively studied  data deduplication techniques can eliminate redundancy 
globally among different files from different users.
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.  Offline deduplication is 
used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%,NGmiddleware2011}.
%Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper}
%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
Several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
As discussed in Section~\ref{sect:intro},
there is no dedicated resource for deduplication in our targeted setting and low memory usage
 is required so that the resource impact to other cloud services is minimized.
%NG et al.~\cite{ NGmiddleware2011}  use
%a related filtering technique for integrating deduplication in Linux  file system and the memory
%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%These are segments that share many chunk IDs with the incoming segment with high probability.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%lookup  
%In comparison, this paper focuses on  full deduplication without approximation.
%We also take advantages of the fact that in a VM cloud environment,
%the virtual device driver can easily keep track if  large data
%segments have been modified using dirty bits and such information can avoid sending
%unmodified data segments for deduplication, which significantly saves cost.

Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
All of the above approaches have focused on
optimization of deduplication efficiency, and none of them have considered the impact
of deduplication for the fault tolerance in the cluster-based environment that we have considered
in this paper.
We will describe the motivation of using the cluster-based   approach
for running the backup service and then present our solution  with fault isolation.
%In our work, the foucs 
%there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
%in our context, finishing the backup of required VM images within a reasonable time window is more
%important than optimizing individual VM block  backup requests.

>>>>

The previous work for storage backup has extensively studied  data deduplication techniques can eliminate redundancy 
globally among different files from different users.
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.  Offline deduplication is 
used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%,NGmiddleware2011}.
%Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper}
%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
Several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
As discussed in Section~\ref{sect:intro},
there is no dedicated resource for deduplication in our targeted setting and low memory usage
 is required so that the resource impact to other cloud services is minimized.
%NG et al.~\cite{ NGmiddleware2011}  use
%a related filtering technique for integrating deduplication in Linux  file system and the memory
%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%These are segments that share many chunk IDs with the incoming segment with high probability.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
to reduce memory requirements with the tradeoff of a reduced deduplication ratio.
%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%lookup  
%In comparison, this paper focuses on  full deduplication without approximation.
%We also take advantages of the fact that in a VM cloud environment,
%the virtual device driver can easily keep track if  large data
%segments have been modified using dirty bits and such information can avoid sending
%unmodified data segments for deduplication, which significantly saves cost.

Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
All of the above approaches have focused on optimization of deduplication
efficiency, and none of them have considered the impact
of deduplication on fault tolerance in the cluster-based environment that we have considered
in this paper.
We will describe the motivation of using the cluster-based   approach
for running the backup service and then present our solution  with fault isolation.
%In our work, the foucs 
%there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
%in our context, finishing the backup of required VM images within a reasonable time window is more
%important than optimizing individual VM block  backup requests.

### 2013-06-21 snapshot_system/result.tex

\section{Experiments}

\subsection{Sampled Index}
One alternative approach to avoiding a single global index is to use a sampled
index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
compare their solution to ours by running their algorithm on our 350 traces
using a sampling rate of 1 out of 101 blocks, and always including the first
block in a container (which we fix at 16MB in size). The results of running this
test are shown in Table~\ref{??}, and the memory usage comparison can be found
Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
rate of deduplication, and so a sampled index might be a good way to do dedup
in a single node setup.

@@

\subsection{Scalable Data Routing}
Another approach to avoiding a global index is to use a content-based hash
partitioning algorithm to break up the deduplication work. This approach is
taken by Dong et al. in their Scalable Data Routing paper, and is similar to
Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
content-based hash partitioning by running the algorithm on our set of 
traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
the minhashes of the superchunks for routing. The results of this are shown in
Table~\ref{??}. Routing each chunk to a bin provides good deduplication
efficiency, and only requires each storage node to keep an index of local data
and the bin mapping, but misses significant opportunities in our indended use
case.

>>>>

\section{Experiments}
Our main test-bed is an cluster of 6 machines,
each of which is equiped with a 8-core AMD FX-8120 at 3.1 GHz
with 16 GB RAM, running Linux.
A distributed file system (QFS) runs in the cluster manages six 3TB disks
 with default replication degree set to 3.
Our data set consists of 350 virtual machine image snapshots taken from Alibaba.com's
public VM cloud in China. We select 35 VMs from the most popular 7 OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
For each OS, 5 VMs are chosen, and every VM come with 10 full snapshots.

\subsection{Comparison with Other Approaches}
\subsubsection{Sampled Index}
One alternative approach to avoiding a single global index is to use a sampled
index. This is the approach taken by Guo and Efstathopoulos\cite{Guo2011}. We
compare their solution to ours by running their algorithm on our 350 traces
using a sampling rate of 1 out of 101 blocks, and always including the first
block in a container (which we fix at 16MB in size). The results of running this
test are shown in Table~\ref{??}, and the memory usage comparison can be found
Sec.~\ref{??}. Our results show that using a sampled index achieves a very high
rate of deduplication, and so a sampled index might be a good way to do dedup
in a single node setup.

@@

\subsubsection{Scalable Data Routing}
Another approach to avoiding a global index is to use a content-based hash
partitioning algorithm to break up the deduplication work. This approach is
taken by Dong et al. in their Scalable Data Routing paper, and is similar to
Exreme Binning\cite{??}\cite{extreme_binning09}. We compared our solution to
content-based hash partitioning by running the algorithm on our set of 
traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
the minhashes of the superchunks for routing. The results of this are shown in
Table~\ref{??}. Routing each chunk to a bin provides good deduplication
efficiency, and only requires each storage node to keep an index of local data
and the bin mapping, but misses significant opportunities in our indended use
case.
